%% ------------------------------ Abstract ---------------------------------- %%
\begin{abstract}
The study of acoustic properties of porous materials has been of interest in many research publications in recent years. Noise pollution is considered to be a major health concern in both homes and places of employment. A means of solving this issue is the use of absorption materials to provide control over the acoustics in a given environment.  As is a trend in many industries, environmentally and biologically friendly materials have become a topic of growing interest. The objective of this research is to present an investigation of Cellulose Acetate Tow (CA) for use as an acoustic absorption material. Analysis of this material was performed via experimental data collected from a Brüel \& Kjær Impedance/Transmission Loss Measurement Tube Type 4206A system to analyze the characteristic absorption coefficient $\alpha_c$ with respect to frequency $f$. The frequency range from $50$ Hz to $6300$ Hz was analyzed. Various form factors of CA have been tested. Experimental results are shown with respect to commercial acoustic absorption media of similar form factor. CA materials with high denier weight have shown similar performance to fiberglass, which is a current standardized material in the industry. Due to the complex nature of porous media absorption problems, the key poroelastic parameters needed for optimization are difficult to identify. As the experimental data reflects, Cellulose Acetate shows promise as an effective alternative to current materials.
\end{abstract}
%% ---------------------------- Copyright page ------------------------------ %%
%% Comment the next line if you don't want the copyright page included.
\makecopyrightpage
%% -------------------------------- Title page ------------------------------ %%
\maketitlepage
%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
\centering{To my Mom, Dad, and Brother.}
\end{dedication}
%% -------------------------------- Biography ------------------------------- %%
\begin{biography}
Sean Casey Maguire was born in Cary, North Carolina on January 11$^\text{th}$, 1991. Sean attended North Carolina State University and received a Bachelor of Science degree in Aerospace Engineering in May 2013. During his undergraduate degree, Sean had the opportunity to travel to Hangzhou, China and Valencia, Spain. While abroad, Sean completed a minor in Spanish Language. His academic career continued at North Carolina State University where he is pursuing a Master of Science degree in Mechanical Engineering.\\
\indent Apart from his research in graduate school, Sean also helped design GUI applications for Mathworks. He works part-time as an Engineering Intern at Cree, Inc. in Durham, North Carolina. In his free time, Sean enjoys music, traveling to new places, basketball, and spending time with his friends.
\end{biography}
%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}
I would like to thank first and foremost my advisor, Dr. Yun Jing for all his guidance and support in my research.\\
\indent I would also like to thank my lab mates in the Acoustics and Ultrasonics Laboratory for their support over the last year of research and classwork.\\
\indent I would like to thank my graduate committee, Dr. Lawrence Silverberg and Dr. Marie Muller for providing valuable input on my thesis and research.\\
\indent Last but not least, I would like to thank, Damon Billodeaux and the entire Eastman Chemical Company Innovation Center, and Aaron Kelley and Auralex Acoustics for their advice and assistance with experiments.
\end{acknowledgements}
\thesistableofcontents
\thesislistoftables
\thesislistoffigures